---
title: "Alcohol vs Seat choice"
author: "Dorothy Decker"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

## Now with ggplot - first select the basic data


```{r}
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Notched Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(hjust = 0.5))

```

  


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
Looking at the average between the alcohol they are drinking is different depending on the seat. In the back they are drinking 9.62, the front are drinking 1.80, and the people in the back are drinking 6.35. This shows the people in the back are consuming more than the other two seats.


## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
```{r}
plot(TukeyHSD(model1))
```

```{r}
# Load the necessary package for ANOVA
library(stats)

# Perform the ANOVA test
anova_result <- aov(alcohol ~ Seat, data = davisdata)

# Check the ANOVA table
anova_table <- summary(anova_result)
print(anova_table)

```



```{r}
# Perform Tukey HSD test
tukey_result <- TukeyHSD(anova_result)

# Print the results
print(tukey_result)
```


Using a second test, we can see there is no difference between the middle and the front according to the plot. But, there is a difference between the back and the other two.



## Conclusions

In conclusion, there is a difference alcohol consumption between those who sit in the back and those who sit in the middle and front. But there isn't a difference between the middle and front.
