---
title: "Alcohol vs Seat choice"
author: "Dorothy Decker"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

## Now with ggplot - first select the basic data


```{r}
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Notched Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(hjust = 0.5))

```

  


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
Looking at the average between the alcohol they are drinking is different depending on the seat. In the back they are drinking 9.62, the front are drinking 1.80, and the people in the back are drinking 6.35. This shows the people in the back are consuming more than the other two seats.


## Inferential Tests

## Conclusions


